\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-08-20 paper/main.tex
corrected notation and wording

\textcolor{blue}{The procedure for computing Bayes factors is described as follows. The Bayes factor computation required us to estimate the marginal likelihood of the competing models. We used the Monte Carlo integration method to estimate the marginal likelihood of each model. First, we chose an importance density for the parameter $F$ from which we draw $0.2$ million samples of $F$. Then, for each of these proposed parameter values, we compute the likelihood and prior density. The estimated marginal likelihood of a model will be given by}

\begin{equation}
ML = \frac{1}{n} \sum_{i=1}{n} \mathcal{L}{F_i|y} p(F_i)  \text{ where } F_i \sim Normal_{lb=0,ub=0.05}(0.0.025) 
\end{equation}

\noindent \textcolor{blue}{where $y$ is the observed data, i.e., the observed semantic interference effect in our case, $F_i$ is the $i^{th}$ proposal from the importance density $Normal_{lb=0,ub=0.05}(0.0.025) $. The term $\mathcal{L}{F_i|y}$ gives the likelihood of proposal $F_i$ given the data $y$ and $p(F_i)$ gives the prior density of $F_i$. We compute marginal likelihoods under different prior assumptions $p(F)$.}

\textcolor{blue}{The Lewis and Vasishth (2005) model is a complex, non-deterministic model and it is difficult to express the model's likelihood analytically without drastically simplifying the model \parencite[e.g., in][]{NicenboimRetrieval2018,lisson2020computational}. In absence of an analytically-expressed likelihood function, we used an Approximate Bayesian Computation (ABC)~\citep{sisson2018handbook,palestro2018likelihood} approach to estimate approximate likelihood for a given value of $F$. Under this approach, we compared the model generated data conditioned on $F=F_i$ and the actual observed data $y$. If the model-generated data $x_{i} \sim Model(F_i)$ for $F_i$ was close to the actual data $y$, then $F_i$ has higher likelihood and vice versa. The likelihood term can be rewritten as $\mathcal{L}{F_i|y} = \Psi(d(x_i, y), 0 , \delta)$, where $\Psi(.|\delta)$ represent a density kernel that weighs a proposal $F_i$ based on distance between model-generated data and actual data, $d(x_i,y)$.}

\textcolor{blue}{From the marginal likelihoods, we computed Bayes factors for the two-cues model compared to the three-cues model and the one-cue model. That is, the marginal likelihood of the two-cues model $M_1$ was divided by the marginal likelihood of the three-cues model $M_2$ and one-cue model $M_3$ to obtain the Bayes factors $BF_{12}$ and $BF_{13}$, respectively. Following the convention from \textcite{jeffreys1998theory}, a Bayes factor above 10 is interpreted as strong evidence in favor of the two-cues model and a value between 3 and 10 is interpreted as moderate evidence in favor of the two-cues model compared to the competing model (see also Table \ref{tab:bf_interpretation}).}

>>>>

\textcolor{blue}{The procedure for computing Bayes factors is as follows. The Bayes factor computation required us to estimate the marginal likelihood of the competing models. We used the Monte Carlo integration method to estimate the marginal likelihood of each model. First, we chose an importance density for the parameter $F$ from which we draw $0.2$ million samples of $F$. Then, for each of these proposed parameter values, we compute the likelihood and prior density. The estimated marginal likelihood of a model will be given by}

\begin{equation}
ML = \frac{1}{n} \sum_{i=1}{n} \mathcal{L}(F_i|y) p(F_i)  \text{ where } F_i \sim Normal_{lb=0,ub=0.05}(0.0.025) 
\end{equation}

\noindent \textcolor{blue}{where $y$ is the observed data, i.e., the observed semantic interference effect in our case, and $F_i$ is the $i^{th}$ proposal from the importance density $Normal_{lb=0,ub=0.05}(0.0.025) $. 
The term $\mathcal{L}{F_i|y}$ gives the likelihood of proposal $F_i$ given the data $y$ and $p(F_i)$ gives the prior density of $F_i$. We compute marginal likelihoods under different prior assumptions $p(F)$.}

\textcolor{blue}{The Lewis and Vasishth (2005) model is a complex, non-deterministic model which can be simplified such that a likelihood function represents the model's generative process  \parencite[e.g., in][]{NicenboimRetrieval2018,lisson2020computational}. However, it is also possible to carry out model comparison without recasting the model as a likelihood function. In this case, model comparison is carried out using Approximate Bayesian Computation (ABC)~\citep{sisson2018handbook,palestro2018likelihood}. Under this approach, the model-generated data conditional on $F=F_i$ is compared with the actually observed data $y$. If the model-generated data $x_{i} \sim Model(F_i)$ for $F_i$ is close to the actual data $y$, then $F_i$ has higher likelihood and vice versa. The likelihood term can be rewritten as $\mathcal{L}(F_i|y) = \Psi(d(x_i, y), 0 , \delta)$, where $\Psi(.|\delta)$ represents a density kernel that weighs a proposal $F_i$ based on the distance between model-generated data $y$ and actual data, $d(x_i,y)$.}

\textcolor{blue}{From the marginal likelihoods, we computed Bayes factors for the two-cues model compared to the three-cues model and the one-cue model. That is, the marginal likelihood of the two-cues model $M_1$ was divided by the marginal likelihood of the three-cues model $M_2$ and one-cue model $M_3$ to obtain the Bayes factors $BF_{12}$ and $BF_{13}$, respectively. Following the convention from \textcite{jeffreys1998theory}, a Bayes factor above $10$ is interpreted as strong evidence in favor of the two-cues model, and a value between $3$ and $10$ is interpreted as moderate evidence in favor of the two-cues model compared to the competing model (see also Table \ref{tab:bf_interpretation}).}
